Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-12 paper.tex
Fixed Frontiers template issues
use begin{abstract}...end{abstract} instead of abstract{...}

While here, restore section numbering.

\abstract{While anthropomorphism in robotics is a commonly discussed trait of
HRI, it paradoxically lacks formal grounds. This article
attempts first at providing a comprehensive synthesis of the social
phenomenon of \textit{perceiving human-like characteristics in non-human
agents and attributing those characteristics to robots}. We draw on
social sciences and psychology, as well as on a critical survey of
existing literature in the HRI community, to ground the concept of
\textit{anthropomorphism}. Supported by extensive literature review
and long-term field studies, we suggest to go beyond the traditional
perception of anthropomorphism as a static feature of a system: we propose to
understand anthropomorphism as a dynamic, non-monotonic and context-dependent
process, which evolves over time and accounts for special events such as the
so-called \textit{novelty effect}. To this end, we introduce a model of
anthropomorphism that analyzes the phenomenon along three interaction phases,
and we discuss cognitive interpretations that follow.
}

%\keywords{Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}

@@

\subsection*{Anthropomorphism as a Social Phenomenon}
\label{sec:social-phenomenon}

@@

\subsection*{Anthropomorphic Design Principle}
\label{sec:anthropomorphic-design}

@@

\subsection*{Anthropomorphism in Robotics and Human-Robot Interaction}
\label{sec:anthropomorphism-robotics}

@@

\subsection*{Multiple factors of anthropomorphism}
\label{sec:multi-factors}

@@

\subsection*{A Model of the Dynamics of Anthropomorphism}
\label{sec:dynamics-model}

@@

\subsection*{Three phases}
\label{sec:phases}

@@

\subsection*{Initialization Phase}
\label{sec:initialization}

@@

\subsection*{Familiarization Phase}
\label{sec:familiarization}

@@

\subsection*{Stabilization Phase}
\label{sec:stabilization}

@@

\subsection*{Cognitive Interpretations}
\label{sec:cognitive-model}

@@

\subsection*{Cognitive Processes and Phases}

@@

\subsection*{Relation to the model of anthropomorphism}

@@

\subsection*{Impact of the behavioral complexity of robots}

@@

\subsection*{Segmentation of interaction phases}

@@

\subsection*{Behavioral cues of anthropomorphism}
\label{sec:behavioralcues}

@@

\subsection*{Effect of Time and Familiarization}

@@

\subsection*{Role of disruptive behaviors}
\label{sec:disruptive}

@@

\vspace{2cm}
\section*{Acknowledgments}

@@

\vspace{2cm}
\section*{Bibliography}

>>>>

\begin{abstract}

While anthropomorphism in robotics is a commonly discussed trait of
HRI, it paradoxically lacks formal grounds. This article
attempts first at providing a comprehensive synthesis of the social
phenomenon of \textit{perceiving human-like characteristics in non-human
agents and attributing those characteristics to robots}. We draw on
social sciences and psychology, as well as on a critical survey of
existing literature in the HRI community, to ground the concept of
\textit{anthropomorphism}. Supported by extensive literature review
and long-term field studies, we suggest to go beyond the traditional
perception of anthropomorphism as a static feature of a system: we propose to
understand anthropomorphism as a dynamic, non-monotonic and context-dependent
process, which evolves over time and accounts for special events such as the
so-called \textit{novelty effect}. To this end, we introduce a model of
anthropomorphism that analyzes the phenomenon along three interaction phases,
and we discuss cognitive interpretations that follow.

\tiny
 \keyFont{ \section{Keywords:} Anthropomorphism, Design, Human-Robot Interaction, Social Issues in Robotics, Acceptance of Robots}

\end{abstract}

@@

\subsection{Anthropomorphism as a Social Phenomenon}
\label{sec:social-phenomenon}

@@

\subsection{Anthropomorphic Design Principle}
\label{sec:anthropomorphic-design}

@@

\subsection{Anthropomorphism in Robotics and Human-Robot Interaction}
\label{sec:anthropomorphism-robotics}

@@

\subsection{Multiple factors of anthropomorphism}
\label{sec:multi-factors}

@@

\subsection{A Model of the Dynamics of Anthropomorphism}
\label{sec:dynamics-model}

@@

\subsection{Three phases}
\label{sec:phases}

@@

\subsection{Initialization Phase}
\label{sec:initialization}

@@

\subsection{Familiarization Phase}
\label{sec:familiarization}

@@

\subsection{Stabilization Phase}
\label{sec:stabilization}

@@

\subsection{Cognitive Interpretations}
\label{sec:cognitive-model}

@@

\subsection{Cognitive Processes and Phases}

@@

\subsection{Relation to the model of anthropomorphism}

@@

\subsection{Impact of the behavioral complexity of robots}

@@

\subsection{Segmentation of interaction phases}

@@

\subsection{Behavioral cues of anthropomorphism}
\label{sec:behavioralcues}

@@

\subsection{Effect of Time and Familiarization}

@@

\subsection{Role of disruptive behaviors}
\label{sec:disruptive}

@@

\vspace{2cm}
\section{Acknowledgments}

@@

\vspace{2cm}
\section{Bibliography}
